\documentclass{article}

%	Encoding
\usepackage[utf8]{inputenc}

%	Language
\usepackage[english]{babel}

%	Blindtext
\usepackage{blindtext}

%	Font
%\renewcommand{\familydefault}{\sfdefault}
%\renewcommand*\sfdefault{phv}
\usepackage[T1]{fontenc}
\usepackage{arev}

% Links
\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor = blue,
}

%	Layout
\usepackage{geometry}
\geometry{
	a4paper,
	left=15mm,
	right=15mm,
	top=15mm
}

%	Remove page's headers, footers, pagenumbers
\pagestyle{empty}

%	Custom section's style
\usepackage{sectsty}
\sectionfont{
	\sectionrule{0pt}{0pt}{-5pt}{1pt}
}
%	List package
\usepackage{enumitem}

%	Multiple columns
\usepackage{multicol}

%----------------------------------------------------------------------------------------

%%	MACROS
%	Size of the box to allign text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

%	Vertical space separator berween entries
\newcommand{\sepspace}{\vspace*{1em}}

%	Name
\newcommand{\name}[1]{
	\Huge	% Font size
	\fontfamily{phv} \selectfont	% Font Family - Helvetica 
	\begin{center}\textbf{#1}\end{center}	% Print the name centered and bold
	\normalsize \normalfont	% Back to normal size and normal font
}

%	Quality	
\newcommand{\quality}[1]{
	\Large
	\fontfamily{phv} \selectfont
	\begin{center}
		\textsc{#1}
	\end{center}
	\par
	\normalsize 
	\normalfont
}

%	Personal Information
\newcommand{\info}[2]{
	\noindent
	\hangindent=2em
	\hangafter=0	% Indentation for personal info
	\parbox{1.5\spacebox}{
		\textbf{#1}	% Slanted entry name 
	}
	: #2 \par	% Entry value
}

\newcommand{\about}[1]{
	% \normalsize
	\noindent
	\textsf{#1}
}

%	Skills
\newcommand{\skill}[2]{
	\noindent\hangindent=2em\hangafter=0	% Indentation for personal info
	\parbox{3\spacebox}{\textsc{#1}}	% Three times larger box
	: #2 \par	% Entry value
	\medskip}	

%	Language level
\newcommand{\lan}[2]{
	\noindent\hangindent=2em\hangafter=0	% Indentation for personal info
	\parbox{1\spacebox}{\textbf{#1}}		% Bold entry name 
	: #2 \par	% Entry value
	\medskip}	

%	Education
\newcommand{\education}[3]{
	\noindent \textbf{#1} \par % Name of the studies
	\noindent\textit{#2} \par	% New paragraph with school in italics
	\vspace*{0.5em}
	\noindent\hangindent=2em\hangafter=0 \small #3	% NO hanging and in smaller text
	\normalsize \par
}

%	Work Experrience
\newcommand{\work}[4]{
	\noindent \textbf{#1} % Name of the work derscription
	\hfill
	\framebox{	% Duration of the work in a box
		\parbox{6em}{
			%\centering\textbf{#2}}} \par
			\centering{#2}}} \par
	\noindent\textit{#3} \par	% New paragraph with work name in italics
	\vspace*{0.5em}
	\noindent\hangindent=2em\hangafter=0 \small #4	% NO hanging and in smaller text
	\normalsize \par
}

%----------------------------------------------------------------------------------------

\begin{document}

	\name{George Papageorgiou}
	\quality{Computer Engineer}
	\bigskip

	\info{Email}{\href{mailto:papageogeo91@gmail.com}{papageogeo91@gmail.com}}
	\info{Phone}{\texttt{+306943185516}}
	\info{Birthdate}{\texttt{28/9/1991}}
	\info{Lives in}{\texttt{Korinthos,Greece}}
	\info{Military}{\texttt{No obligation}}
	\info{Github}{\url{https://github.com/ramonrulez}}
	\bigskip

	\about{
		I am Computer Engineer with passion for software development. My background in various technical fields equipped me with problem-solving skills, adaptive reflexes and a holistic approach in technical problems.
	I am currently working in my dissertation in Computer Engineering and looking for ways to leverage my skills and gain more knowledge in the field of Software Development.
	}
	\section*{Work Experience}
	\work{Electronic components assembly specialist / RnD specialist}{2019--2024}{\href{https://smartmoto-electronics.com/}{SmartMoto Electronics}}{
		\begin{center}
			My job was to develop and manufacture electronics for motorbikes.
		\end{center}
		\begin{multicols}{2}	
			The manufacturing included:
			\begin{itemize}[noitemsep]
				\item SMD soldering,
				\item wiring looms and accesorries,
				\item assembly of microelectronics,
				\item processing of aluminum slabs.
			\end{itemize}
			\columnbreak
			
			The development part included:
			\begin{itemize}[noitemsep]
				\item developing software to automate tasks,
				\item prototyping of electronic circuitry,
				\item new products prototyping,
				\item assignments for the development of the company.
				\item AVR microcontrollers prototyping
			\end{itemize}
		\end{multicols}
	}
	\sepspace

	\work{Technician / Assistant Audio Engineer}{2017--}{\href{https://www.wreckitsoundstudios.com/}{Wreck IT Sound Studios}}{
		\begin{center}
			The purpose of the job was to care for the technical function of the studio
		\end{center}
		\begin{multicols}{2}
			The main workload of the job included:
			\begin{itemize}[noitemsep]
				\item cable soldering,
				\item repairing mixing consoles and audio gear,
				\item guitar maintanance, setup and repair,
				\item development of audio gear,
				\item audio engineering,
				\item recording engineering.
			\end{itemize}
		\end{multicols}
	}
	\sepspace

	\work{Technician}{2015--2019}{\href{https://supertvkorinthos.gr/}{Super TV Korinthos}}{
		\begin{center}
			The work in the TV station included the management of 4 local and peripheral TV stations.
		\end{center}
		\begin{multicols}{2}
			The primary responsibilities was:
			\begin{itemize}[noitemsep]
				\item maintaining the programm flow,
				\item video Editing in Edius,
				\item camera work, indoors or outdoors.
			\end{itemize}
		\columnbreak

		Furthermore sometimes occured tasks like:
		\begin{itemize}[noitemsep]
			\item directing LIVE broadcasts and shows,
			\item sound recording,
			\item gear maintainance,
			\item LIVE streaming on Youtube and Facebook.
		\end{itemize}
		\end{multicols}
	}

	% Break until next page for the rest
	\pagebreak

	\section*{Education}
	\education{Computer Engineering and Informatics Department(CEID)}{University of Patras}{Currently in the phase of dissertation.}
	\sepspace
	\education{High School}{3o High School of Korinthos}{}


		\section*{Skills}
			\skill{Programming Languages}{\textsl{C/C++, PHP, Javascript, SQL, JAVA, MATLAB}}
			\skill{Scripting}{\textsl{Bash, Python}}
			\skill{Markup}{\textsl{HTML, CSS, }\LaTeX\textsl{ ,XML}}
			\skill{Other}{\textsl{Linux, git}}
			\skill{Soldering}{\textsl{Through Hole, SMD}}
			\skill{Guitar Technician}{\textsl{Setup, Maintanance, Live Support}}
			\skill{Soft Skills}{\textsl{Problem Solving, Adaptability, Creativity, Diligence, Ambition}}
			\skill{Driving Licence}{\textsl{Type B}}
			
		\section*{Languages}
			\lan{Greek}{Native}
			\lan{English}{C2}


\end{document}
